MA_Results

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
up to fw

<!-- Add aims text here -->
In this paper, we introduce a framework for developing youth mental health OSHEMs. Specifically we describe:

- a set of guidelines for implementing OSHEMs;

- a toolkit for applying these guidelines in youth mental health; and

- a worked example of a modelling project developed with the toolkit.

>>>>

<!-- Add aims text here -->
In this paper, we introduce a framework for developing a modular youth mental health MOSHEM. Specifically we:

(i) describe a framework that is comprised of:
  - a set of standards for implementing a MOSHEM; and
  - a modelling toolkit (repositories and software) to author MOSHEM modules, supply them with data and undertake reproducible analyses consistent with those standards.

(ii) provide a worked example of how we used the framework to develop and apply MOSHEM modules for utility mapping.

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
up to fw

Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems. <!-- such as Git [@git20XX].  --> Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are **TIMELY** (Transparent, Iterative, Modular, Epitomising, Licensed and Yielding - see Table \@ref(tab:timelygls)).

@@

## Transparent models
A range of tools and practices are available to help make models more transparent. The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020] to make permanently accessible and uniquely identfied digital artefacts. <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item. These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022]. Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases. -->Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012]. <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.  --><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].  -->Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same type. Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->to render documents that integrate computer code with plain English descriptions.

An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019]. One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested. <!-- In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics. -->Finally, transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020]. The risk of these errors might be lower if there was full transparency across all steps in a study workflow. Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].

@@

## Iterative models
To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.  Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.   <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable. For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers. The online platform GitHub [@github2007] can make this version history accessible to anyone. -->Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data. <!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g. ExampleSoftware v1.1.1.1). Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.  -->Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. <!-- OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.  --><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).  -->
Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.  
<!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->

@@

## Modular models
An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either. Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].

## Epitomising models
A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.

Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017]. When bundled for distribution as libraries<!-- (for example, as R packages) -->, functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for. A special type of function, called a method, can only be applied to a pre-defined class of data structure. Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022]. For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.Whatever type of functions are written for a modelling project, it is good practice to make available test or toy data to demonstrate their use [@Wilson_2017].

<!-- - **E2: Model code defines inheriting data-structures** -->

## Licensed models
```{r echo = F}
gpl_pc_dbl <- get_license_share("GPL")
```

To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions. In the context of open source models, there are two broad categories of licensing options. Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used. An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements.The most suitable approach may differ for code and data.

For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used. <!-- Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license. -->For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022]. Responsible custodianship of some de-identified mental health data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants). Licenses may or may not specify that model re-users must give appropriate acknowledgement to model authors. Citation tools can be distributed with each individual code or data item to inform re-users of the desired attribution. 
<!-- In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021]. More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021]. Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers. -->

## Yielding models
OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use. Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users. 
<!-- In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020]. -->

>>>>

Based on published guidance on computational modelling in health economics and other disciplines and our own experience, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards). The standards are specified in Table \@ref(tab:timelygls) and are discussed below.

@@

### Standards for an accountable MOSHEM
Guidance on transparency in health economic modelling published over ten years ago [@Eddy2012] made recommendations on documenting models but notably did not include recommendations on sharing model code and data. However, more recent and multidisciplinary healthcare modelling guidance [@Erdemir2020] recommends using existing digital repository services to these types of digital model artefacts. Some types of repository such as GitHub [@github2007] provide tools for disseminating work in progress code and providing highly transparent records of the complete development history and individual authorship contributions of a software project, while others such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.

Model code and data should be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012]. <!-- nd --> Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same type. Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->that integrate computer code with plain English descriptions.

An essential component of quality assuring health economic models is verification - ensuring that calculations are correct and consistent with model specifications [@techver2019]. One useful concept for informing model users about the extensiveness of verification checks is code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested. <!-- In R, the testthat [@testthat2011] and covr [@covr2020] tools can be used in conjunction with GitHub to define tests and report coverage metrics. -->Transcription errors - mistakes introduced when transferring data between sources, models and reports - are very common in health economic models [@Radeva2020]. The risk of these errors might be lower if there was full transparency across all steps in a study workflow. Scientific computing tools now make it relatively straightforward to author programs that reproducibly execute all steps in data ingest, processing and reporting [@Wilson_2017].

Code and data should be distributed with tools that make it easy for potential users to appropriately cite each model artefact.

@@

<!-- and the use of version control systems. <!-- such as Git [@git20XX].  -->  
<!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item. These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022]. Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases. --> <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.  --><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].  -->

### Standards for a reusable MOSHEM
<!-- ## Licensed models -->
```{r echo = F}
gpl_pc_dbl <- get_license_share("GPL")
```

To make model code and data widely re-usable by others, it is important to provide users with appropriate and explicit permissions. In the context of open source models, there are two broad categories of licensing options. Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which the content could be re-used. An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open source arrangements. For code, it may be appropriate to adopt the prevailing open source licensing practice within the programming language being used. For data, it may not be sufficient to simply choose between a permissive license like the Public Domain Dedication (CC0) [@cc02022] or a copyleft option such as the Attribution-Share Alike (CC-BY-SA) [@bysa2022]. In addition to ensuring that data is ethically appropriate for disseminate in open access repositories, responsible custodianship of some de-identified or aggregated data may involve using or adapting template terms of use [@sampleterms2022] which have a number of ethical clauses (for example, prohibiting efforts to re-identify research participants).

Storing and managing model code and data separately, can make it easier to apply models to different decision contexts and, when necessary, to selectively restrict access to data that are confidential, while disseminating all other model artefacts. Clear distinctions should be made between model modules (code that defines abstract data structures and the algorithms that can be applied to data described by these structures), model datasets (digital information such as parameter values, unit records, etc) and model analyses (code that specifies the data to be supplied to modules and selects which module algorithms to apply to that data).

The coding practice of encapsulation [@8717448] can be used to help ensure that model modules can be safely combined [@ready4oop2022]. In some cases, combining modules may mean new versions of modules have to be created that account for their effects on each other. The coding concept of inheritance [@8717448] can be used to efficiently achieve this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022]. Writing algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017]. Functions to implement model algorithms can be associated with module data structures (also known as a class) via a special type of function called a method. Model modules of a similar type or purpose can be efficiently distributed and documented by bundling them as code libraries. It is good practice to make available test or toy data to demonstrate the use of model algorithms [@Wilson_2017].

<!-- When bundled for distribution as libraries<!-- (for example, as R packages) -->
<!-- , functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for.  --> 
<!-- A special type of function, called a method, can only be applied to a pre-defined class of data structure.  -->

<!-- ## Yielding models --><!-- MOSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use.  -->
Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users. In the open source R language, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020].

<!-- Applying a previously published algorithm [@kross2016] to analyse the most comprehensive archive of released R packages [@CRAN2022] finds that `r gpl_pc_dbl`% are distributed under various forms of General Public License (GPL) [@GNUGPL2022], a copyleft license. -->
<!-- In R, including a CITATION file in the `inst` directory of a package will enable users of that package to retrieve citation information by running a command of the format `citation("Package Name")` in the R console [@Salmon2021]. More generally, including a CITATION.cff file at the top level of your code repository will enable GitHub and Zenodo repositories hosting that item to include the relevant information in their citation tools [@Druskat_Citation_File_Format_2021]. Datasets hosted on Dataverse installations have metadata fields that, once completed by authors, generate citation files for dataset viewers. -->

<!-- A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.  -->
<!-- For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.  -->
<!-- Guidelines: -->

<!-- - **E2: Model code defines inheriting data-structures** --> <!-- Order changed-->

### Standards for an updatable MOSHEM
To avoid MOSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.  Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020]. Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data. Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.

<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.   <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable. For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers. The online platform GitHub [@github2007] can make this version history accessible to anyone. -->

<!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g. ExampleSoftware v1.1.1.1). Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.  -->
<!-- MOSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.  --><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).  -->

<!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->

@@

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
up to fw

---
title: "MS_Imp_Guidelines"
output: html_document
date: '2022-07-21'
---
<!-- # Framework -->
<!-- The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards. -->

We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.

## Repositories <!-- Existing ref -->
We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022]. To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022]. Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].

@@

A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].

As a foundation for implementing the framework, we authored a development version R package that defines a novel syntax and a template class for model modules [@ready42022]. To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:

- documented model modules [@ready4class2022];

@@

- citable, quality assured R packages [@ready4pack2022];

@@

The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs). When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 16 of the TIMELY standards. However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4). Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software. Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].

>>>>

---
title: "MS_Imp_Guidelines"
output: html_document
date: '2022-07-21'
---
<!-- # Framework -->
<!-- The framework we have developed to implement **readyforwhatsnext** specifies standards for MOSHEMs and provides tools for meeting those standards. -->

We have developed a toolkit to help streamline the process of developing and using MOSHEMs that meet the standards listed in Table \@ref(tab:timelygls). The toolkit is comprised of online repositories and software.

## Repositories <!-- Existing ref -->
We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022]. That was linked to an account we set up at code codecov [@codecov_2022] for tracking our unit tests and the Zenodo community [@ready4zen2022] we created to store citable archived copies of release copies of our software. Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].

@@

<!-- A coding framework for MOSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->

As a foundation for implementing our framework, we authored a development version R package that defines a template class for model module data structures [@ready42022] and a novel syntax for implementing the algorithms that will be attached to model modules. To enable the syntax and module template be applied to modelling projects, we then created five additional development version R packages that provide tools for authoring:

- documented model module data-structures [@ready4class2022];

@@

- citable, quality assured module libraries [@ready4pack2022];

@@

The six R packages, their primary focus, the framework standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs). When used in conjunction with framework repositories, the six packages extend existing R packages provide strong support for implementing 17 of the framework standards. However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standard for deprecation conventions (I4). Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software. Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
up to fw

There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models. Users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].  This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models. Value judgments strongly shape health economic analyses, yet are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey]. A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses [@thompson2022escape]. As health economic models adopt more sophisticated techniques, the need for accountability grows. More complex models may be more prone to propagation errors [@Saltelli2019] and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations [@Eddy2012; @Feenstra2022]. The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape].

<!-- Many health economic models are released with errors [@Radeva2020]. -->
<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
<!-- Accountability for both the scientific quality and social acceptability of health economic models can be improved.  -->
<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->

Collaborative approaches that encourage re-use of models by other modellers can help make modelling pojects more tractable [@Arnold2010]. However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022]. Not all data included in health economic models can be ethically made publicly available due to privacy and confidentiality requirements. Transferring a health economic model developed for one jurisdiction for application in another will involve retaining some features and updating others [@barbieri2010international]. Use of concepts with standardised meanings across jurisdictions [@garcia2021cost], supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works are all steps that can enhance model transferability.

@@

Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017]. Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year. A model can grow stale when changes in the real world, whether sudden (e.g. new pandemics) or gradual (e.g. demographic), is not represented by corresponding updates to relevant model features. Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation. Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements. The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.

@@

A modular approach to model building involves models being constructed by combining multiple replaceable sub-models (modules) [@pan2021modular]. When used as model sub-components, modules communicate with other modules but they can be also run independently [@barros2023empowering]. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular]. Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], neuroscience [@frazier2022robust] and ecology [@barros2023empowering]. Although the related and enabling concept of reusable reference models has been recommended in health economics [@Afzali2013], peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in tuberculosis [@Trauer2017] and cardiology [@Urach2013].

<!-- A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components. -->

<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
The benefits of modular models can be enhanced if multiple modelling teams have the capacity to contribute and use model modules. To facilitate this, modular models may be implemented as open source projects that grant liberal permissions to access and re-use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust]. Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].

@@

We plan to develop a modular OSHEM of youth mental health. Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022]. 
<!-- that rarely explores complex dynamic systems  -->
<!-- [PECUNIA] -->

>>>>

There is a strong case for making health economists more accountable for the appropriate use and social acceptability of their models. Users of models should be able to assess their adequacy for a particular purpose [@thompson2019escape].  This goal is difficult to achieve in the current context of the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017] and frequently insufficient validation [@Ghabri2019] of health economic models. Many health economic models are released with undeclared errors [@Radeva2020]. The value judgments that strongly shape health economic analyses are rarely made explicit, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey]. A modelling team's value judgments about what questions to address, the most important features of a system to represent and the weighting of different types of evidence may be poorly aligned with those of the people impacted by decisions informed by model analyses [@thompson2022escape]. As health economic models adopt more sophisticated techniques, the need for accountability grows. More complex models may be more prone to propagation errors [@Saltelli2019] and models designed to address multiple questions should be expected to meet more onerous verification and validation obligations [@Eddy2012; @Feenstra2022]. The nature and extent of individual model authorship contributions may be less clear in models implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape].

<!-- As modelling methods have become more sophisticated, some have argued that more complex models are required to adequately explore certain types of public health topics [@SQUIRES2016588].  -->
<!-- Accountability for both the scientific quality and social acceptability of health economic models can be improved.  -->
<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->

The resource and skills intensive undertaking of modelling could be made more tractable if it was easier for health economists to re-use each other's models [@Arnold2010]. However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022]. Legal and ethical issues such as privacy and confidentiality requirements further limit public release of some model artefacts [@Pouwels2022]. Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international]. However, models do not always make implementation choices (for example, use of concepts with standardised meanings across jurisdictions<!-- [@garcia2021cost] -->, supplying context specific data as replaceable data-packs and distributing source code under licenses that allow derivative works) that facilitate model transferability.

@@

Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017]. Funding for health economic modelling projects rarely extend to provision of medium term support for model updates and improvements. The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model and / or from working on the health condition for which the model was developed.
<!-- Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year.A model can grow stale when changes in the real world, whether sudden (e.g. new pandemics) or gradual (e.g. demographic), is not represented by corresponding updates to relevant model features. Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation.  -->

@@

A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular]. Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], neuroscience [@frazier2022robust] and ecology [@barros2023empowering]. In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].

<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->
Modular models provide an opportunity for multiple modelling teams to contribute to, test and reuse models. To enhance this capacity, modular models may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust]. Although there appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs)  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].

@@

We plan to develop a modular OSHEM (MOSHEM) of youth mental health that is accountable, reusable and updatable. Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].

<!-- that rarely explores complex dynamic systems  -->
<!-- [PECUNIA] -->

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
up to fw

```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->

# Guidelines
```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
```

# Framework
```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
```

>>>>

```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->
# Framework
<!-- Modular and open source models from other disciplines are enabled by standardisation and software.  -->
To help us implement a MOSHEM in youth mental health, we have developed a framework that:

- specifies a set of standards for MOSHEM development and use; and

- provides a modelling toolkit (repositories and software) for authoring model modules, managing data and implementing reproducible analyses consistent with those standards.

## Standards
```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
```

## Modelling toolkit
```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
```
